---
title: "Iteration and Listcols"
author: "Ravi Brenner"
date: "2024-10-29"
output: github_document
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(rvest)
set.seed(1)
```

## some lists
```{r}
l <- list(
  vec_numeric = 1:4,
  unif_sample = runif(100),
  mat = matrix(1:8, nrow = 2, ncol = 4, byrow = TRUE),
  summary = summary(rnorm(1000))
)

l

#ways to access elements of the list
l$mat
l[["mat"]]
l[[3]]
```

make a list that's a bit more useful
```{r}
list_norm = 
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 4, 10)
  )

list_norm[["b"]]
```

reuse a function we wrote last time
```{r}
mean_and_sd <- function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for vectors of length 1")
  }
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x)
}
```

use the function to take mean and sd of all samples
```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])
```

## use a for loop
Could turn this into a loop (especially if we have a much larger list)

create output list, and run a for loop
```{r}
output <- vector("list", length = 4)

for (i in 1:4){
  output[[i]] = mean_and_sd(list_norm[[i]])
}
```

And better yet, turn that loop into a `map` function

```{r}
output = map(list_norm, mean_and_sd)
```

try a few other things

can use any function
```{r}
output = map(list_norm, IQR)
output
```

can map_TO specific things
```{r}
output = map_dbl(list_norm, IQR)
output

output = map_dfr(list_norm, mean_and_sd)
output
```

## List columns




