---
title: "Iteration and Listcols"
author: "Ravi Brenner"
date: "2024-10-29"
output: github_document
---

```{r setup, warning=FALSE, message=FALSE}
library(tidyverse)
library(rvest)
set.seed(1)
```

## some lists
```{r}
l <- list(
  vec_numeric = 1:4,
  unif_sample = runif(100),
  mat = matrix(1:8, nrow = 2, ncol = 4, byrow = TRUE),
  summary = summary(rnorm(1000))
)

l

#ways to access elements of the list
l$mat
l[["mat"]]
l[[3]]
```

make a list that's a bit more useful
```{r}
list_norm = 
  list(
    a = rnorm(20, 0, 5),
    b = rnorm(20, 4, 5),
    c = rnorm(20, 0, 10),
    d = rnorm(20, 4, 10)
  )

list_norm[["b"]]
```

reuse a function we wrote last time
```{r}
mean_and_sd <- function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for vectors of length 1")
  }
  mean_x = mean(x)
  sd_x = sd(x)
  
  tibble(
    mean = mean_x,
    sd = sd_x)
}
```

use the function to take mean and sd of all samples
```{r}
mean_and_sd(list_norm[["a"]])
mean_and_sd(list_norm[["b"]])
mean_and_sd(list_norm[["c"]])
mean_and_sd(list_norm[["d"]])
```

## use a for loop
Could turn this into a loop (especially if we have a much larger list)

create output list, and run a for loop
```{r}
output <- vector("list", length = 4)

for (i in 1:4){
  output[[i]] = mean_and_sd(list_norm[[i]])
}
```

And better yet, turn that loop into a `map` function

```{r}
output = map(list_norm, mean_and_sd)
```

try a few other things

can use any function
```{r}
output = map(list_norm, IQR)
output
```

can map_TO specific things
```{r}
output = map_dbl(list_norm, IQR)
output

output = map_dfr(list_norm, mean_and_sd)
output
```

## List columns

```{r}
listcol_df <- tibble(
  name = c("a","b","c","d"),
  samp = list_norm
)

listcol_df 

listcol_df |>
  filter(name %in% c("a","b"))



listcol_df |>
  select(-samp)
```

extract one in a sort of naive way
```{r}
listcol_df[["samp"]][["a"]]
```

compute mean and sd
```{r}
mean_and_sd(listcol_df[["samp"]][["a"]])

map(listcol_df[["samp"]], mean_and_sd)
```

Better to create a new column that has these results (i.e. a list column)
```{r}
listcol_df |>
  mutate(output = map(samp, mean_and_sd),
         iqr = map_dbl(samp, IQR)) |>
  select(-samp) |>
  unnest(output)
```

## NSDUH data example

```{r}
nsduh_table_format = function(html, table_num) {
  
  out_table = 
    html |> 
    html_table() |> 
    nth(table_num) |> 
    slice(-1) |> 
    select(-contains("P Value"))
  
  return(out_table)
  
}
```

now need to import the html, then extract correct tables
```{r}
nsduh_url = "http://samhda.s3-us-gov-west-1.amazonaws.com/s3fs-public/field-uploads/2k15StateFiles/NSDUHsaeShortTermCHG2015.htm"

nsduh_html = read_html(nsduh_url)
```

```{r}
nsduh_table_format(html = nsduh_html, table_num = 1)
nsduh_table_format(html = nsduh_html, table_num = 4)
nsduh_table_format(html = nsduh_html, table_num = 5)
```

```{r}
nsduh_df = tibble(
  drug = c("Marijuana","Cocaine","Heroin"),
  table_n = c(1,4,5)) |>
  mutate(table = map(table_n, nsduh_table_format, html = nsduh_html)) |>
  unnest(table)

# a slightly different way to use the map function
nsduh_df = tibble(
  drug = c("Marijuana","Cocaine","Heroin"),
  table_n = c(1,4,5)) |>
  mutate(table = map(table_n, \(x) nsduh_table_format(html = nsduh_html, table_num = x))) |>
  unnest(table)

nsduh_df |>
  filter(State == "New York")
```


## weather data example
```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USW00022534", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2021-01-01",
    date_max = "2022-12-31") |>
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USW00022534 = "Molokai_HI",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) |>
  select(name, id, everything())
```

create a list column
```{r}
weather_nest <- 
  weather_df |>
  nest(data = date:tmin)
```

```{r}
weather_nest[["data"]][1]
```

try regressing tmax on tmin
```{r}
lm(tmax ~ tmin, data = weather_nest[["data"]][[1]])
lm(tmax ~ tmin, data = weather_nest[["data"]][[2]])
lm(tmax ~ tmin, data = weather_nest[["data"]][[3]])
```

But the better way to do this
```{r}
weather_nest |>
  mutate(model_fit = map(data, \(x) lm(tmax ~ tmin, data = x)),
         model_stats = map(model_fit, broom::tidy))  |>
  unnest(model_stats)
```


